---
name: Faith
surname: Frings
position: "PhD Candidate"
address: "105 Main St, Durham, NH 03824"
www: faithfrings.github.io
email: "Faith.Frings@unh.edu"
#to get the orcid: 0000-0001-6087-0428
googlescholar: QulnQpwAAAAJ&hl
osf: nrtbk # currently vitae doesn't support osf in the yaml header, need to add \osf{nrtbk} in the .tex file manulaly
github: faithfrings
# twitter: \_HanZhang_
#researchgate: Han_Zhang175
headcolor: 414141 # use black color
date: "`r format(Sys.time(), '%B %Y')`"
csl: apa-cv.csl # change this if you want to use other citation styles
output: 
  vitae::awesomecv:
      keep_tex: false
      pandoc_args: ["--lua-filter=lua/names.lua", "--template=awesome-cv.tex"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble)
#rmarkdown::pandoc_version()
```

# Education

```{r}
tribble(
  ~ Degree,
  ~ Advisor,
  ~ Year,
  ~ Institution,
  #PhD
  "Doctor of Philosophy, Integrative Biology",
  "Advisor: Dr. Melissa Aikens | Dissertation: Building data literate biologists: Investigating student motivational dynamics in statistical programming across diverse biology courses",
  "08/2022-present",
  "University of New Hampshire",
  #Master's
  "Master of Science, Biology with a concentration in ecology and evolution",
  "Advisor: Dr. Luanna Prevost | Thesis: Mixed-method analysis of undergraduate student interpretation of different phylogenetic tree styles",
  "08/2020-08/2022",
  "University of South Florida",
  #Bachelor's
  "Bachelor of Science, Marine Biology",
  NA,
  "08/2017-05/2020",
  "University of South Florida",
) %>%
  detailed_entries(
    with = Degree,
    where = Year,
    what = Institution,
    why = Advisor
  )
```

# Research Experience

## Dissertation (2022 - present)
Advised by Dr. Melissa Aikens
```{r}

research <- tribble(
  ~What,
  ~Duty,

  "Characterizing student R programming motivation and engagement",
  c(
    "Conducted multilevel modeling to examine changes in students' motivation to learn R programming",
    "Conducted path analysis to investigate relationships among students' R programming mindsets, task values, and effort on R programming tasks"
  ),

  "Examining student R programming motivation across course types",
  c(
    "Collected and analyzed open-response survey data to identify factors shaping students' motivation across R-integrated biology courses"
  ),

  "Exploring student motivation to learn data science in the field",
  c(
    "Collected and analyzed semi-structured interviews to identify factors shaping students' motivation to learn R programming in a field-based data science course"
  ),

  "Factors explaining student R programming resource use in biological research",
  c(
    "Collected and analyzed semi-structured interviews, participant observations, and surveys to examine how and why students select resources when programming in a biological research course"
  )
)
research %>%
  detailed_entries(
    what = What,
    why = Duty
  )
```

## Thesis (2020 - 2022)
Advised by Dr. Luanna Prevost
```{r}
research <- tribble(
  ~What,
  ~Duty,
 "Examining student phylogenetic tree interpretations across tree styles",
  c(
    "Conducted thematic analysis, phi correlations, and Mann-Whitney U tests of open-response data to characterize undergraduate students' reasoning across different phylogenetic tree styles"))

research %>%
  detailed_entries(
    what = What,
    why = Duty
  )
```

## Undergraduate Research (2019 - 2020)
Advised by Dr. Luanna Prevost
```{r}
research <- tribble(
  ~What,                                           
  ~Duty,
  "Student reasoning about food webs", c(
    "Conducted thematic analysis and phi correlations of open-response data examining students' interpretations of food webs"
  ))
research %>%
  detailed_entries(
    what = What,
    why = Duty
  )
```

## Graduate Research Assistant

```{r}
research <- tribble(
  ~When,       ~With,                                          ~What,                                           ~Duty,
  "2022-2026", "Biology Education Research Group (BERG), UNH", "Community college transfer student persistence", c(
    "Conducted semi-structured interviews and thematic analysis to investigate supports and barriers experienced by community college transfer students at a four-year institution"
  ),

  "2022-2026", "Biology Education Research Group (BERG), UNH", "Student graphical reasoning", c(
    "Conducted thematic analysis of open-response data to characterize students' graphical reasoning"
  ),

  "2022", "Prevost Lab, USF", "Amgen biotechnology education project", c(
    "Developed online instructional resources for biology educators through an Amgen Foundation-funded biotechnology education project"
  )
)

research %>%
  detailed_entries(
    when = When,
    with = With,
    what = What,
    why = Duty
  )
```

# Teaching Experience

## Primary Instructor

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Duty,
  '06/2026',
  "BIOSM 2350/MEFB 633: R by the Sea: Data Analysis in Marine Sciences",
  "undergraduate, 1 summer term"
) %>%
  detailed_entries(where = Year,
                   with = Name,
                   what = Duty) 
```

## Graduate Teaching Assistant

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Duty,
  '2023 - 2026',
  "BIOL 706/806: Data Science for Life Sciences",
  "Undergraduate/graduate, 4 semesters",
  '2023 - 2026',
  "BIOL 528: Applied Biostatistics ",
  "Undergraduate, 4 semesters",
  '2025',
  "BIOSM 3290/MEFB 714: Field Animal Behavior",
  "Undergraduate, 1 summer term",
  '2024',
  "BIOSM 4990/MEFB 751: Research in Biology",
  "Undergraduate, 1 summer term",
  '2024',
  "BIOSM 1610/MEFB 674: Ecology & the Marine Environment",
  "Undergraduate, 1 summer term",
  "2022",
  "BIOL 412: Introductory Biology Laboratory",
  "Undergraduate, 1 semester",
  '2022',
  "BSC 2011: Biology II – Biological Diversity",
  "Undergraduate, 1 semester",
  '2020 - 2021',
  "BSC 2011L: Biology II – Biological Diversity Laboratory",
  "Undergraduate, 2 semesters",
  '2021',
  "BSC 1005: Biological Principles for Non-Majors",
  "Undergraduate, 1 semester"
) %>%
  detailed_entries(where = Year,
                   with = Name,
                   what = Duty) 
```

## Workshops

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Duty,
  '01/2026',
  "R by the Sea - Japan. Advanced Institute for Marine Ecosystem Change (WPI-AIMEC), Tohoku University.",
  "co-taught a five-day introductory r and statistics workshop"
) %>%
  detailed_entries(where = Year,
                   with = Name,
                   what = Duty) 
```

## Invited lectures

```{r}
bibliography_entries("bibs/invited_talks.bib")
```

## Invited facilitator

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Duty,
  '2026',
  "Professional Development in Evidence-Based Teaching Series (PDET)",
  ""
) %>%
  detailed_entries(where = Year,
                   with = Name,
                   what = Duty) 
```

# Teaching Distinctions & Professional Development

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Duty,
  '2025',
  "UNH Graduate Student Excellence in Teaching Award",
  "Recognition by the Department of Biological Sciences for teaching achievement",
  '2019,22,25',
  "Human Subjects Research Certificate",
  "Web-based course modules on responsible conduct of human subjects research"
) %>%
  detailed_entries(where = Year,
                   with = Name,
                   what = Duty) 
```

# Journal Articles

```{r}
bibliography_entries("bibs/journal_articles.bib")
```

# Book Chapters 

```{r}
bibliography_entries("bibs/other.bib")
```

# Media

```{r}
bibliography_entries("bibs/media.bib")
```


# Presentations
Underlined names indicate undergraduate research mentees.
```{r}
bibliography_entries("bibs/conference_presentations.bib")
```

# Research Mentoring

## Undergraduate Mentees

```{r}
tribble(
  ~ Year,
  ~ What,
  '2026',
  "Ashley Greene",
  '2025-2026',
  "Carleigh Koopman",
  '2025',
  "Abigail Dearth",
  '2025',
  "Ava Prieto",
  '2023-2024',
  "Sara Amovic",
  '2023-2025',
  "MeiLing Maddox",
  '2022 - 2023',
  "Virginia Weiss"
) %>%
  detailed_entries(when = Year,
                   what = What) 
```

# Awards & Fellowships
```{r}
tribble(
  ~Year, ~Name, ~Institution, ~Supp, ~Amount,
  '2025',
  'Student Teaching Award Fellowship',
  'UNH Graduate School, University of New Hampshire',
  NA,
  '$2000',
  
  '2024', 
  'Bill Woods Graduate Student Poster Award',
  'Society for the Advancment of Biology Education Research annual meeting', 
  '',
  '$500',
  
  '2024, 2025', 
  'Travel Award', 
  "Department of Biological Sciences, University of New Hampshire",
  NA,
  '$800',
  
  '2024, 2026', 
  "Travel Award",
  "UNH Graduate School, University of New Hampshire",
  NA,
  '$800',
  
  '2020-2021',
  'S-STEM Scholarship',
  "Integrative Biology Department, University of South Florida",
  NA,
  "$5,600"
) %>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Institution,
    why = Supp,
    when = Amount
  ) 
```


# Grants in Support of Research

```{r}
tribble(
  ~Year, ~Name, ~Institution, ~Supp, ~Amount,
  '2025',
  'Graduate Student Research Fund', 
  'School of Marine Sciences and Ocean Enginnering, University of New Hampshire',
  NA, 
  '$998',
)%>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Institution,
    why = Supp,
    when = Amount
  ) 
```

# Professional Service

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Duty,
  '2023-present',
  "UNH R Users Group Organizer",
  "Organize and lead weekly R Users Group meetings",
  '2025 - 2026',
  "SABER Virtual Day Conference Committee",
  "Co-developed and co-hosted the inaugural Virtual Day of the 16th SABER annual meeting",
  '2025-2026',
  "SABER Discipline-Based Education Research-Scholars in Training (DBER-SiT) Chair",
  "Organized and delegated DBER-SiT committee projects",
  "2024-2025",
  "SABER DBER-SiT Chair-elect",
  "Shadowed and assisted the Chair in their role",
  '2023-2025',
  "SABER DBER-SiT Funding Co-chair",
  "Identified and disseminated funding sources for DBER-scholars in training",
  '2023-2026',
  "UNH Undergraduate Research Conference Poster Judge",
  "Evaluated quality of research and design of undergraduate life sciences research posters",
  '2022-2024',
  "UNH DBS Graduate Student Committee",
  "Co-founded the committee; organized graduate student seminar series; hosted outreach events"
) %>%
  detailed_entries(where = Year,
                   what = Name,
                   why = Duty) 
```

# Manuscripts Reviewed

Tips, Tricks, and Techniques in the American Biology Teacher

# Technical Skills

- **Programming:** R (advanced)
- **Quantitative methods:** Multilevel modeling, structural equation modeling
- **Qualitative methods:** Thematic analysis, cross-case analysis, semi-structured interview protocol development, participant observation, open-response item development
- **Reproducible research:** R Markdown, Quarto
- **Version control:** Git/GitHub

# References

```{r}
tribble(
  ~ Name,
  ~ Title,
  ~ Contact,
  'Melissa Aikens, Ph.D.',
  "Department Associate Chair, Associate Professor of Biology Education; University of New Hampshire",
  "Melissa.Aikens@unh.edu",
  'Easton White, Ph.D.',
  "Associate Professor, Department of Biological Sciences, Associate Director of Research, School of Marine Science and Ocean Engineering, University of New Hampshire",
  "Easton.White@unh.edu",
  'Luanna Prevost, Ph.D.',
  "Tampa Campus Associate Chair, Associate Professor, Department of Integrative Biology, University of South Florida",
  "prevost@usf.edu"
) %>%
  detailed_entries(where = Contact,
                   with = Name,
                   what = Title) 
```
